Compiling refinement types to dependent types

### 2020-07-22 tex/paper.tex
Lift out the remark for \hat B

@@

    Here we somewhat frivolously use $\hat B$ to denote
    the core language analogue of the surface language base type $B$.
    For example, if this rule is instantiated for $B$ equal to $\Unit$,
    then $\hat B$ would be $\Unitc$.

    We also do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}

>>>>

In addition to that, we will somewhat frivolously use $\hat B$
to denote the core language analogue of a surface language base type $B$,
which exists for $\Unit$ ($\hat B$ then being $\Unitc$)
and which we assume to exist for any other surface language base type
mentioned in \cref{remark:surface_base_types}.

@@

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}
